---
title: "NYC Restaurant Inspection Dashboard Code"
output: html_document
---


This document contains the code for the [dashboard of NYC Restaurant inspection](rest_inspec_dashboard.html) data from 2012 to 2017. We begin by loading the following packages

```{r, message = FALSE, warning = FALSE}
library(flexdashboard)
library(p8105.datasets)
library(plotly)
library(tidyverse)
```


We load the data with the `p1805` data sets package. We clean the date variable and create a variable for the restaurant being closed as a result of the inspection.
```{r}
rest_inspec = 
  p8105.datasets::rest_inspec |> 
  mutate(
    year_month = str_sub(inspection_date, 0, 7),
    year = year(inspection_date),
    month = year(inspection_date),
    closed_flag = action %in% c(
      "Establishment Closed by DOHMH.  Violations were cited in the following area(s) and those requiring immediate action were addressed.",
      "Establishment re-closed by DOHMH")
    )
```



### Inspection Grades over Time

```{r}
rest_inspec |>
  drop_na(grade, score) |> 
  filter(grade %in% c('A', 'B', 'C')) |> 
  group_by(year_month) |> 
  count(grade) |> 
  plot_ly(x = ~year_month, y = ~n, color = ~grade, type = 'scatter', mode = 'line')|> 
  layout(xaxis = list(title = 'Time'),
         yaxis = list(title = 'Number of Grades Issued'))
```


### Inspection Scores by Grade 

```{r}
rest_inspec |> 
  drop_na(score) |> 
  filter(grade %in% c('A', 'B', 'C')) |> 
  group_by(grade)|> 
  plot_ly(x = ~grade, color = ~grade, y = ~score, type = 'box' )|> 
  layout(xaxis = list(title = 'Grade'),
         yaxis = list(title = 'Score'))
```


### Proportion of Inspections Resulting in Restaurant Closure by Borough

```{r}
rest_inspec |> 
  filter(boro != 'Missing') |> 
  group_by(boro) |> 
  summarize(perc_closed = mean(closed_flag)) |> 
  plot_ly(x = ~boro, y = ~perc_closed, color = ~boro, type = "bar") |> 
  layout(xaxis = list(title = 'Borough'),
         yaxis = list(title = 'Proportion'))
```